Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2022-09-27 response-reviewers-2.tex

After consideration, the authors agree with the comment and we have replaced teachers for Tutorship in the keywords.

% -> answer 4

{\it 4.      If the article is concerned with research activity, has a sound methodology been utilized and described? A sound methodology was utilized and described. However, it was observed that prior studies have not previously validated the measurement instrument used in collecting data. Thus, the authors need to conduct reliability and validity tests for their proposed measurement instrument used in collecting data.}

The authors thank the reviewer for pointing out that flaw which was addressed, improving the quality of the paper.

A new subsection whithin the methodology (Section 3.1 Survery validation) deals with the procedure to validate the tests by using a board of experts for the questionaire.

@@

    b. TO DO

%%%%%% Rev 4

{\bf Reviewer \#4}: {\it First of all, this paper seems to be the main topic of 'Analysis from the teacher's perspective of chatbots and messaging platforms in class'.
It seems that simple survey results were analyzed and grouped.
It seems like a lot of effort was put into it, but I doubt whether it has any academic significance.
Why did you choose 4 questions? Is it appropriate for a chatbot and messaging platform if I just ask and group this? I am not sure.
Looking at the research results and conclusions, there are some contents that are difficult to see as valid because the evidence for the researcher's conclusions is so abrupt and abstract.}

The authors thank the reviewer for provinding useful feedback to improve the quality of the paper.

Regarding the first issue (the lack of academic significance), we want to stress the importance of the topic of how AI tools are going to modify our lifestyle in the comming years. This study shares experiences from the academic and educational point of view and analyses the results obtained. Nonetheless, the Introduction (as well as other sections) has been rewritten with the hope of addressing the academic significance in a clearer way.

Regarding the validation of the methodology, there is a new subsection that presents the validation procedure by means of an expert board which agrees with the procedure and contents presented.

For the final comment, we have rewritten the conclusions and abstract to improve the way the content is explained.

### 2022-09-27 edubots_surveys.Rnw
new subsection 3.1 for survey validation and new answers to reviewers

>>>>

\subsection{Survey validation}
\textcolor{blue}{

To avoid any bias and to be sure about the quality of the questionnaire, a panel board was consulted. There were three items for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
Clarity was measured as an answer to the question: Is the item well presented and without ambiguity? \footnote{Original text: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: Yes or No. 
Both Importance and Adequateness were measured in a Likert scale from 1 to 4 (1 low, 4 high).

The panel board was composed by 7 volunteer experts that have wide experience as educators and researchers. The results obtained are summarized in Table \ref{tab:validation}.

As validation shows, all expert agree without any doubt about the clarity of each question. Furthermore, there is a large consensus regarding the Importance and Adequateness of all the eight questions in the questionnaire.

\begin{table}
\begin{tabular}{|c|ccc|}
    \hline
    Questions & Clarity (Yes/No) & Avg. Importance & Avg. Adequateness \\
    \hline
    Q1 &  Yes (100\%)  &  3,571 (0,53) & 3,571 (0,53) \\
    Q2 &  Yes (100\%)  &  3,714 (0,49) & 3,571 (0,53) \\
    Q3 &  Yes (100\%)  &  3,857 (0,38) & 3,857 (0,38) \\
    Q4 &  Yes (100\%)  &  3,571 (0,79) & 3,857 (0,38) \\
    Q5 &  Yes (100\%)  &  3,714 (0,49) & 3,714 (0,49) \\
    Q6 &  Yes (100\%)  &  3,714 (0,49) & 3,857 (0,38) \\
    Q7 &  Yes (100\%)  &  3,714 (0,49) & 3,714 (0,49) \\
    Q8 &  Yes (100\%)  &  4 (0) & 4,000 (0) \\
    \hline
\end{tabular}
\caption{Validation results from the panel board (7 experts) for each question in the research questionnaire. The range of values for Importance and Adequateness is from 1 to 4 (higher is better).}\label{tab:validation}
\end{table}
